Top Private Equity Firms with Larger Average Fund Sizes and Lower Internal Rate of Returns (IRRs) in the United States Give ESG a Higher Importance

### 2024-04-18 paper/paper.qmd
Completed Data Section

library(tidyverse)
library(palmerpenguins)
library(here) 
library(knitr)
library(janitor)
library(arrow)
```

@@

Next, the ESG score was calculated using the methodology detailed above. After doing so, all the columns used in its calculation were also deleted since they were not needed anymore, leaving the final data set looking like FIGURE 10.

```{r}
#| label: fig-1
#| echo: false
#| warning: false
#| message: false
#| fig-cap: "Total Number of Funds vs ESG Score"
#| fig-pos: H

analysis_data <- read_csv("data/analysis_data/cleaned_data1.csv")

ggplot(analysis_data, aes(x = Totalnumberoffunds, y = ESG_Score)) +
  geom_point() +
  labs(x = "Total Number of Funds", 
       y = "ESG Score", 
       title = "Total Number of Funds vs ESG Score")

@@

>>>>

library(tidyverse)
library(palmerpenguins)
library(here) 
library(knitr)
library(janitor)
library(arrow)
library(here)
library(gridExtra)

analysis_data <- read_csv(here("data/analysis_data/cleaned_data1.csv"))
```

@@

Next, the ESG score was calculated using the methodology detailed above. After doing so, all the columns used in its calculation were also deleted since they were not needed anymore. A snippet of the first 10 firms is seen in @tbl-1. Moreover, @fig-2, @fig-4, @fig-3 demonstrate the correlations between each firm characteristics, and their ESG Score.

```{r}
#| label: tbl-1
#| echo: false
#| warning: false
#| message: false
#| tbl-cap: "First 10 Private Equity Firms in the cleaned dataset"
#| tbl-pos: H

analysis_data |>
  mutate(
    Sum_wirr_preqin = round(Sum_wirr_preqin, 2),
    Average_Fund_Size = round(Average_Fund_Size, 2)
  ) |>
  head(10) |>
  kable(
    col.names = c("Firm", "No. of Funds", "Fund Size", "IRR", "Staff", "Average Fund Size", "ESG Score")
  )

@@

```{r}
#| label: fig-2
#| echo: false
#| warning: false
#| message: false
#| fig-cap: "ESG Score by IRR and Staff Count"
#| fig-pos: H

irr <- ggplot(analysis_data, aes(x = Sum_wirr_preqin, y = ESG_Score)) +
  geom_point() +
  labs(title = "Internal Rate of Return vs ESG Score",
       x = "Internal Rate of Return",
       y = "ESG Score") +
  theme_minimal() + 
  theme(plot.title = element_text(hjust = 0.5, size = 10),
                axis.title.x = element_text(size = 9),
                axis.title.y = element_text(size = 9),
        axis.text.y = element_text(size = 7.5))

staff <- ggplot(analysis_data, aes(x = Staff_Count, y = ESG_Score)) +
  geom_point() +
  labs(title = "Number of Employees vs ESG Score",
       x = "Number of Employees",
       y = "ESG Score") +
  theme_minimal() + 
  theme(plot.title = element_text(hjust = 0.5, size = 10),
                axis.title.x = element_text(size = 9),
                axis.title.y = element_text(size = 9),
        axis.text.y = element_text(size = 7.5))

grid.arrange(staff, irr, 
               ncol = 2
)
```

```{r}
#| label: fig-4
#| echo: false
#| warning: false
#| message: false
#| fig-cap: "ESG Score by IRR and Staff Count"
#| fig-pos: H

number_of_funds <- ggplot(analysis_data, aes(x = Totalnumberoffunds, y = ESG_Score)) +
  geom_point() +
  labs(title = "Total Number of Funds vs ESG Score",
       x = "Total Number of Funds",
       y = "ESG Score") +
  theme_minimal() + 
  theme(plot.title = element_text(hjust = 0.5, size = 10),
                axis.title.x = element_text(size = 9),
                axis.title.y = element_text(size = 9),
        axis.text.y = element_text(size = 7.5))

size <- ggplot(analysis_data, aes(x = FundSize_Preqin, y = ESG_Score)) +
  geom_point() +
  labs(title = "Fund Size vs ESG Score",
       x = "Fund Size",
       y = "ESG Score") +
  theme_minimal() + 
  theme(plot.title = element_text(hjust = 0.5, size = 10),
                axis.title.x = element_text(size = 9),
                axis.title.y = element_text(size = 9),
        axis.text.y = element_text(size = 7.5))

grid.arrange(number_of_funds, size, 
               ncol = 2
)
```

```{r}
#| label: fig-3
#| echo: false
#| warning: false
#| message: false
#| fig-cap: "ESG Score by Average Fund Size"
#| fig-pos: H

ggplot(analysis_data, aes(x = Average_Fund_Size, y = ESG_Score)) +
  geom_point() +
  labs(title = "Average Fund Size vs ESG Score",
       x = "Average Fund Size",
       y = "ESG Score") +
  theme_minimal() + 
  theme(plot.title = element_text(hjust = 0.5, size = 10),
                axis.title.x = element_text(size = 9),
                axis.title.y = element_text(size = 9),
        axis.text.y = element_text(size = 7.5)) 
    plot.margin = unit(c(0.1, 0.1, 0.1, 0.1), "cm")
